Process-based phenotypes: an application to the ontology of cell physiology

### 2011-11-28 paper/drinking.tex
added captions

  \caption{\label{fig:patterns}Six examples of processes with
    non-comparative and comparative process attributes.  We assume
    that the processes labelled $a$, $b$, $c$ and $d$ are all
    instances of the class of processes $P$.  On the left side, three
    regulation (of $P$) processes are illustrated which exhibit
    non-comparative attributes. The first process has an attribute of
    {\em rhythmic} occurrence of $P$ because the instances of $P$ are
    temporally equidistantly distributed. The second example shows an
    {\em arrhythmic} occurrence of $P$, and the third examples shows
    an {\em increasing frequency} (of $P$). A regulation process with
    an increasing frequency (of $P$) is a process in which the
    frequency of occurrences of $P$ is lower in the first half of the
    process than in the second...}
\end{figure}

>>>>

  \caption{\label{fig:patterns}Six examples of processes with
    non-comparative and comparative process attributes.  We assume
    that the processes labelled $a$, $b$, $c$ and $d$ are all
    instances of the class of processes $P$.  On the left side, three
    regulation (of $P$) processes are illustrated which exhibit
    non-comparative attributes. The first process has an attribute of
    {\em rhythmic} occurrence of $P$ because the instances of $P$ are
    temporally equidistantly distributed. The second example shows an
    {\em arrhythmic} occurrence of $P$, and the third examples shows
    an {\em increasing frequency} (of $P$). A regulation process with
    an increasing frequency (of $P$) is a process in which the
    frequency of occurrences of $P$ is lower in the first half of the
    process than in the second half. The right side of the figure
    illustrates comparative phenotypic descriptions of processes. On
    the upper right, the {\em normal} reference is shown. The second
    example illustrates a {\em late onset} of $P$, i.e., the attribute
    that $P$ processes begin later than {\em normal}. Finally, the
    lower right illustrates a {\em decreased frequency} (of $P$),
    since fewer processes of the type $P$ occur within the reference
    process than {\em normal}.}
\end{figure}
